A Machine Learning Approach to Kinematic Synthesis of Defect-Free Planar Four-Bar Linkages

### 2018-04-25 idetc2018_conf_version.tex
Some more corrections

In this paper, we 1) employ pattern recognition and computational shape analysis, to create a similarity transforms-independent signature for coupler path and motion, 2) exploit the non-linear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
We define a novel objective function for defect-free motion generation problems and present an algorithm for partial matching of motions.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
The Fig.~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.

@@

The above methods generate data based on uniform sampling in the linkage parameter space.
Given highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a non-uniform sampling of trajectory space causing under-representation of possible motions.
We address this issue by employing log-normal distribution in the linkage parameter space to generate data and perform compact clustering of the data using machine learning techniques.
Hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
In contrast to this, we need to store only one curve representing all the segments in it as our representation facilitates partial matching.
None of the other previous methods facilitate this partial matching of open motion curve into another open or closed curve, which significantly contributes to providing a large number of solutions, and reduces the data requirement even further.

@@

Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$.
Here, $\theta(t)$ represents the change in orientation along the path, measured with respect to initial orientation and is not restricted in the domain $[-\pi, \pi]$.

@@

\subsection{Partial Matching of Path Signatures}\label{sec_ncc}
When a path query is raised, it can be very useful to know whether this path matches with the part of a path from the database.
This subsection presents a method for determining this partial similarity.

@@

Here, $p$ acts as a template that tries to find the best match against $W$ while sliding over it along $j$.
Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment of $p$ inside $W$.

@@

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_whole_part.eps}
  \caption{Part path is formed by trimming whole path followed by translation and scaling.}
\label{wholePart}
\end{figure}

>>>>

In this paper, we 1) employ pattern recognition and computational shape analysis, to create a similarity transform-independent signature for coupler path and motion, 2) exploit the non-linear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.
When a user inputs a motion or a path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
We define a novel objective function for defect-free motion generation problems and present an algorithm for partial matching of motions.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
The Fig.~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.

@@

The above methods generate data based on uniform sampling in the linkage parameter space.
Given highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a non-uniform sampling of trajectory space causing under-representation of possible motions.
We address this issue by employing log-normal distribution in the linkage parameter space to generate data and perform compact clustering of the data using machine learning techniques.
Hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
In contrast to this, we need to store only one curve representing all the segments in it, as our representation facilitates partial matching.
None of the other previous methods facilitate this partial matching of open motion curve into another open or closed curve, which significantly contributes to providing a large number of solutions, and reduces the data requirement even further.

@@

Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$.
Where, $\theta(t)$ is the change in orientation along the path with respect to initial orientation.
It should be noted that $\theta(t)$ is a continuous curve with domain ($-\infty$, $\infty$) in contrast to conventional domain i.e. [$-\pi$, $\pi$].

@@

\subsection{Partial Matching of Path Signatures}\label{sec_ncc}
When a path query is raised, it can be very useful to know whether this path matches with a part of a path from the database.
This subsection presents a method for determining this partial similarity.

@@

Here, $p$ acts as a template that tries to find the best match against $W$ while sliding over it along $j$.
Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment\footnote{\emph{Path} is identical to a portion of \emph{Whole}.} of $p$ inside $W$.

@@

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/fig_whole_part.eps}
  \caption{\emph{Part} path is formed by trimming whole path followed by translation and scaling. Arrows indicate the increasing direction of parameter $t$.}
\label{wholePart}
\end{figure}
